A multi-scalar model for system of cities

### 2019-10-01 Docs/Communications/2019/CCS2019/Communication/slides.tex
slides_just_in_time

\sframe{Modeling urban growth}{

@@

@@

@@

\textbf{\textit{Urban multi-scalar complexity must be capture by a strongly coupled model}}

@@

$\rightarrow$ no strongly coupled multi-scalar model in the literature

@@

\begin{itemize}
 \item Model: \texttt{https://github.com/JusteRaimbault/UrbanGrowth-model}
 \item Project: \texttt{https://github.com/JusteRaimbault/UrbanGrowth}
 \item Simulation data: \texttt{}% dataverse
\end{itemize}

>>>>

\sframe{Urban growth across time and scales}{

@@

\includegraphics[width=0.48\textwidth]{figures/ConceptPlan1971.jpg}\hspace{0.1cm}
\includegraphics[width=0.48\textwidth]{figures/ConceptPlan1991.jpg}\\
\includegraphics[width=0.48\textwidth]{figures/2001-CONCEPTPLAN.jpg}\hspace{0.1cm}
\includegraphics[width=0.48\textwidth]{figures/conceptplan2011.jpeg}

@@

$\rightarrow$ Distinct processes and objects within each different scale

@@

\textbf{\textit{Urban multi-scalar complexity must be captured by a strongly coupled model}}

@@

$\rightarrow$ no strongly coupled multi-scalar model in the literature (few examples such as \cite{murcio2015urban} but without distinct ontologies)

@@

\begin{itemize}
 \item Model: \texttt{https://github.com/JusteRaimbault/UrbanGrowth-model}
 \item Project: \texttt{https://github.com/JusteRaimbault/UrbanGrowth}
 \item Simulation data: \texttt{https://doi.org/10.7910/DVN/IRHMQK}% dataverse
\end{itemize}
